\chapter{Conclusion}
\section{Conclusion}

The project has shown, that RMI is a way of making a group of PC's and other java devices work together. 
The RMI is a good and reliable way to connect a group of pc devices, and creates a good way to communicate. Through the leader election it can create a reliable(meaning: that it holds always has a leader, that is up to date, no matter what happens) leader selection, that secures that the network is always functional.

It has show in our prototype, that it is easy to create a RMI connection, and use it. There was a problem getting the connection to work properly, since when the connection was created, it could not get the ???? to ????. This was solved by giving ??? to the ???, and then it worked both by creating to network, and setting new leaders when needed to.

\section{Discussion}
The project work with the subject RMI has been more difficult compared to DNS and DDS.
Implementation and setup has caused problems and the group has struggled to make a prototype work.
The theoretical part of RMI was divided among the members of the group, whereas each group member would write in the report.

Making a prototype like this is relevant, because...

Discuss your project work.

\section{Perspectives}
How does the RMI support network communication within pc networks?
The RMI makes it posible to create a interface, and 
What makes the RMI relevant to consider, when we are speaking network communication?

What are the perspectives on the technology and your prototype? 